A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-26 main.tex
Finished section 3.

\begin{definition}[Values]
	$A \neq \epsilon$\\
	\begin{align*}
		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{and } A' \neq \epsilon)                           & \\
		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
	\end{align*}
\end{definition}

\begin{definition}[Staged Reduction]
	$A \neq \epsilon$\\
	\begin{align*}
		E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
		E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
		E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
	\end{align*}
\end{definition}

\begin{definition}[Evaluation Context]
	$A \neq \epsilon$\\
	\begin{align*}
		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B
		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
		\mid E^\epsilon_B\ \epsilon                                                                                                \\
		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B
		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                   \\
		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B
		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                               \\
	\end{align*}
\end{definition}

>>>>

\begin{definition}[Values]
	The family $V^A$ of sets of values, ranged over by $v^A$ and 
	the sets of $\epsilon$-redexes (ranged over by $R^\epsilon$) and $\alpha$-redexes (ranged over by $R^\alpha$)
	are defined by following grammar. In the grammar $A \neq \epsilon$.
	\begin{align*}
		\textrm{Values}  &  & v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon                                       & \\
		                 &  & v^A \in V^A               & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} \mid \Lambda\alpha.v^A \mid v^A\ \epsilon & \\
		                 &  &                           & \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon)                           & \\
		                 &  &                           & \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A)                                                           & \\
		\textrm{Redexes} &  & R^\epsilon                & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon                                       & \\
		                 &  & R^\alpha                  & ::=\ \TBL_\alpha \TB_\alpha M                                                                                      & \\
	\end{align*}
\end{definition}

Values at $\epsilon$ stage are a $\lambda$ abstraction, a quoted code, or a $\Lambda$ abstraction.
The body of a $\lambda$ abstraction can be any term but the body of $\Lambda$ abstraction only can be a value.
This restriction means that the body of $Lambda$ abstraction must evaluated before application of an $\epsilon$ stage.
Values at non-$\epsilon$ stage includes all term except $\TBL_\alpha v^\epsilon$.
This is because $\TBL_\alpha v^\epsilon$ is a redex.

\begin{definition}[Evaluation Context]
	The family of sets $ECtx^A_B$ of evaluation contexts, ranged over by $E^A_B$, is defined by the following grammar,
	$A$ is nonempty. (Although $B,A'$ can be empty.)
	$A \neq \epsilon$\\
	\begin{align*}
		E^\epsilon_B \in ECtx^\epsilon_B & ::= \square\ (\text{if\ } B = \epsilon) \mid E^\epsilon_B\ M \mid v^e\ E^\epsilon_B
		\mid \TB_\alpha E^\alpha_B \mid \Lambda\alpha.E^\epsilon_B
		\mid E^\epsilon_B\ \epsilon                                                                                                \\
		E^A_B \in ECtx^A_B               & ::= \square\ (\text{if } A = B) \mid \lambda x:\tau.E^A_B \mid E^A_B\ M \mid v^A\ E^A_B
		\mid E^\epsilon_B \mid \TB_\alpha E^{A\alpha}_B
		\mid \TBL_\alpha E^{A'}_B \ (\text{where } A'\alpha = A)                                                                   \\
		                                 & \quad \mid \Lambda\alpha.E^\epsilon_B
		\mid E^A_B\ \epsilon \mid \%_\alpha\ E^{A'}_B \ (\text{where } A'\alpha = A)                                               \\
	\end{align*}
\end{definition}

We write $E^A_B[M]$ for a term obtained by filling the hole in $E^A_B$ with $M$.

\begin{definition}[Staged Reduction]
	The staged reduction relation, written $M \longrightarrow_s M'$, is defined by 
	the least relation closed under the rules in Figure \ref{fig:staged-reduction}.
\end{definition}

\begin{figure}
	\begin{center}
		\begin{align*}
			E^A_\epsilon [(\lambda x:\tau.M)\ v^\epsilon]       & \longrightarrow_s E^A_\epsilon[M[x\mapsto v^\epsilon]]             \\
			E^A_\epsilon [(\Lambda\alpha.v^\epsilon)\ \epsilon] & \longrightarrow_s E^A_\epsilon[v^\epsilon[\alpha\mapsto \epsilon]] \\
			E^A_\alpha [\TBL_\alpha \TB_\alpha v^\alpha]        & \longrightarrow_s E^A_\alpha[v^\alpha]                             \\
		\end{align*}
		\caption{Staged Reduction}
		\label{fig:staged-reduction}
	\end{center}
\end{figure}
